---
title: ""
output: html_document
---
<style>
    /* Global Styles */
    body {
        font-family: Arial, sans-serif;
        background-color: #000; /* Black background */
        color: #fff; /* White text */
        text-align: center;
        margin: 0;
        padding: 20px;
        box-sizing: border-box;
    }
    h1 {
        font-size: 2rem; /* Dynamic font size */
    }
    h3 {
        font-size: 1.6rem; /* Dynamic font size */
    }
    p {
        font-size: 1.2rem; /* Dynamic font size */
    }
    /* Dropdown menu */
    select {
        padding: 10px;
        font-size: 1rem;
        background-color: #333; /* Dark dropdown background */
        color: #fff; /* White text in dropdown */
        border: 1px solid #555; /* Gray border */
        width: 100%; /* Full width on smaller devices */
        max-width: 400px; /* Max width for larger screens */
        margin: 10px auto; /* Centered */
    }
    select:focus {
        outline: none;
        border: 1px solid #fff; /* White border on focus */
    }
    /* Button */
    button {
        padding: 10px 20px;
        margin-top: 20px;
        font-size: 1rem;
        background-color: #444; /* Dark button background */
        color: #fff; /* White text */
        border: 1px solid #666; /* Gray border */
        cursor: pointer;
        width: 100%; /* Full width on smaller devices */
        max-width: 400px; /* Max width for larger screens */
    }
    button:hover {
        background-color: #555; /* Lighter color on hover */
    }
    /* Logo */
    #teamLogoContainer {
        display: flex;
        justify-content: center; /* Center horizontally */
        align-items: center; /* Center vertically */
        margin-top: 20px;
        display: none; /* Hidden by default */
    }
    #teamLogo {
        width: 50px; /* Fixed size for the logo */
        height: 50px; /* Fixed size for the logo */
        display: none; /* Hidden by default */
    }
    /* Media Queries for iPhones */
    @media (max-width: 480px) {
        h1 {
            font-size: 1.8rem;
        }
        h2 {
            font-size: 1.4rem;
        }
        p {
            font-size: 1rem;
        }
        button, select {
            font-size: 1rem;
            padding: 8px 16px;
        }
        #teamLogo {
            width: 50px; /* Ensure fixed size remains consistent */
            height: 50px;
        }
    }
    .accordion {
  background-color: yellow;
  color: #3b3c41;
  cursor: pointer;
  padding: 10px;
  width: 100%;
  border: none;
  text-align: center;
  outline: none;
  font-size: 5px;
  transition: 0.4s;
}
.active, .accordion:hover {
  background-color:black;
  color:yellow;
}
.accordion:after {
  content: '\2795';
  color: black;
  font-weight: bold;
  float: right;
  font-size: 20px;
  margin-left: 15px;
}
.active:after {
  content: "\2212";
  color: yellow;
  font-weight: bold;
}
.panel {
  padding: 0 10px;
  background-color: #3b3c41;
  max-height: 0;
  overflow: hidden;
  transition: max-height 0.2s ease-out;
}
</style>
<body>
  <h1>Data Analysis</h1>
  <p>Choose a team to navigate to its page:</p>
  <!-- Dropdown menu -->
  <select id="teamSelect" onchange="showLogo()">
      <option value="" data-logo="images/BerlinerSC.png">-- Select a Team --</option>
      <option value="BSC.html" data-logo="images/BSC.png">Berliner SC</option>
      <option value="Rudow.html" data-logo="images/TSVRudow.png">TSV Rudow Berlin</option>
      <option value="SternBritz.html" data-logo="images/SternBritz.png">Stern Britz</option>
  </select>
  <br>
  <!-- Logo placeholder -->
  <div id="teamLogoContainer">
      <img id="teamLogo" src="" alt="Team Logo">
  </div>
  <button onclick="navigateToTeam()">Go</button>
```{r setup, include=FALSE}
# Setzt den Cache auf FALSE für alle Chunks im Dokument
knitr::opts_chunk$set(cache = FALSE)
library(tidyverse)
library(dplyr)
library(data.table)
library(ggplot2)
library(knitr)
library(ggforce)
# Install and load formattable if not already installed
devtools::install_github("haozhu233/kableExtra")
if (!require(formattable)) install.packages("formattable")
library(formattable)
library("kableExtra")

matchday_data <- read_csv("/Users/mkreuschnervsp/Desktop/BSC/Spieltag11.csv")

```
```{r include=FALSE}
# Define the URL of the csv.gz file and the destination file path
matchday_data <- read_csv("/Users/mkreuschnervsp/Desktop/BSC/Spieltag11.csv")
player_data <- read.table("/Users/mkreuschnervsp/Desktop/BSC/fupa2425_player_data_11.csv", sep=",", header=TRUE, stringsAsFactors = FALSE, fileEncoding = "UTF-8")
player_number <- read.csv("/Users/mkreuschnervsp/Desktop/BSC/player_number.csv")  # Replace with your CSV file path
max_matchday <- max(matchday_data$matchday)  # Calculate max matchday
# Calculate the new columns and add them to the player data
player_number_info <- player_number %>%
  select(ID, Nummer) 
player_data <- merge(player_data, player_number_info, by = "ID", all.x = TRUE)

player_data <- player_data %>%
  mutate(
    # First column: Spielzeit divided by (90 * max_matchday), or 0 if Spiele is 0
    playtime_ratio = ifelse(Spiele == 0, 0, round(Spielzeit / (90 * max_matchday), 3)),
    
    # Second column: Spielzeit divided by Spiele, then by 90, or 0 if Spiele is 0
    avg_playtime_per_game = ifelse(Spiele == 0, 0, round(Spielzeit / (Spiele * 90), 3)),
    
    # Third column: (Tore + Assists) divided by Spiele, or 0 if Spiele is 0
    scorerpoints_per_game = ifelse(Spiele == 0, 0, round((Tore + Assists) / Spiele, 3))
  )

# Step 1: Extract last names from `Name` in `player_data`
player_data <- player_data %>%
  mutate(last_name = word(Name, -1))  # Extract last word from Name as last name

# Step 2: Extract best players and count appearances from games_data
# Split 'best_players' by comma, remove leading/trailing spaces, and count each player's occurrences
best_player_counts <- matchday_data %>%
  filter(!is.na(best_players)) %>%
  mutate(best_players = str_split(best_players, ",\\s*")) %>%  # Split by comma and trim whitespace
  unnest(best_players) %>%                                      # Expand each player into separate rows
  group_by(best_players) %>%
  summarise(best_player_appearances = n())                      # Count each player's "best player" appearances

# Step 3: Join with player_data using last names and calculate the ratio of "best player" appearances to total games played
player_data <- player_data %>%
  left_join(best_player_counts, by = c("last_name" = "best_players")) %>%  # Join by last name
  mutate(
    best_player_appearances = coalesce(best_player_appearances, 0),        # Replace NA with 0 for players with no appearances
    best_player_ratio = ifelse(Spiele == 0, 0,                             # Calculate ratio; if Spiele is 0, set to 0
                               round(best_player_appearances / Spiele, 3))
  ) %>%
  select(-last_name)  # Remove the last_name helper column if it's no longer needed

# Step 1: Calculate team points based on game results
data <- matchday_data %>%
  mutate(
    team_points = case_when(
      goals_s > goals_c ~ 3,    # 3 points for a win
      goals_s == goals_c ~ 1,   # 1 point for a draw
      goals_s < goals_c ~ 0     # 0 points for a loss
    )
  )

# Step 2: Extract player participation, handling both main players and substitutes
player_participation <- data %>%
  select(matchday, team, squad, team_points) %>%
  
  # Step 2.1: Extract all player names inside parentheses, remove numbers and symbols, and store them
  mutate(substitute_names = str_extract_all(squad, "\\([A-Za-z\\s]+\\)")) %>%
  mutate(substitute_names = lapply(substitute_names, function(x) {
    x <- str_replace_all(x, "[()]", "")           # Remove parentheses
    x <- str_trim(str_squish(x))                  # Trim whitespace
    x <- str_split(x, ",\\s*")                    # Split multiple names by commas
    unlist(x)                                     # Unlist to get all names in a single vector
  })) %>%
  
  # Step 2.2: Remove all content inside parentheses from the original squad string
  mutate(squad = str_remove_all(squad, "\\([^\\)]+\\)")) %>%
  
  # Step 2.3: Split the squad by commas and "–" to get main player names
  mutate(squad = str_split(squad, ",\\s*|–")) %>%
  
  # Step 2.4: Combine main and substitute player names into a single column
  rowwise() %>%
  mutate(all_players = list(c(squad, substitute_names))) %>%
  unnest(all_players) %>%                                # Expand each player into a separate row
  mutate(
    all_players = str_trim(all_players)                  # Ensure no whitespace issues
  ) %>%
  
  # Step 2.5: Remove duplicates and calculate participation
  distinct(all_players, matchday, .keep_all = TRUE) %>%  # Ensure unique player names for each match
  group_by(all_players) %>%
  summarise(
    total_points = sum(team_points, na.rm = TRUE),       # Sum points for each player's games
    matches_played = n_distinct(matchday)                # Count unique matches played
  ) %>%
  
  # Rename 'all_players' to 'squad' to reflect player names for compatibility with joining
  rename(squad = all_players)

# Step 1: Ensure `last_name` is correctly extracted from `Name` in `player_data`
player_data <- player_data %>%
  mutate(last_name = str_trim(word(Name, -1)))  # Extract and trim last names for matching

# Verify that `last_name` was added correctly
print(head(player_data$last_name))  # Check if `last_name` exists as expected

# Check unique last names in both tables before joining
print("Unique last names in player_data:")
print(unique(player_data$last_name))

print("Unique squad names in player_participation:")
print(unique(player_participation$squad))

# Step 2: Perform the left join and handle missing columns
player_data <- player_data %>%
  left_join(player_participation, by = c("last_name" = "squad")) %>%  # Join on last name
  mutate(
    # Add missing columns if they do not exist after the join
    matches_played = ifelse(is.na(matches_played), 0, matches_played),  # Set to 0 if missing
    total_points = ifelse(is.na(total_points), 0, total_points),        # Set to 0 if missing
    match_diff = Spiele - matches_played,                               # Difference between Spiele and matches_played
    points_per_game = ifelse(matches_played == 0, 0,                    # Calculate points per game
                             round(total_points / matches_played, 3)),
    normalized_points_per_game = round(points_per_game / 3, 3)          # Divide by 3 and round to 3 decimals
  ) %>%
  select(-last_name)  # Remove helper last_name column
```
```{r include=FALSE}
# Define weights for Score
weight_playtime_ratio <- 0.3
weight_avg_playtime_ratio <- 0.2
weight_scorerpoints_per_game <- 0.1
weight_best_player_ratio <- 0.3
weight_normalized_points_per_game <- 0.1
```
```{r include=FALSE}
# Define formation positions and coordinates for plotting (rotated 90 degrees)
formation_positions <- list(
  "4-4-2" = data.frame(
    Position = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST", "ST"),
    x = c(50, 30, 40, 60, 70, 25, 40, 60, 75, 40, 60),  # New x coordinates (original y)
    y = c(5, 15, 25, 25, 15, 35, 50, 50, 35, 70, 70)    # New y coordinates (original x)
  ),
  "4-3-3" = data.frame(
    Position = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "LM", "ST", "ST", "ST"),
    x = c(50, 30, 40, 60, 70, 50, 30, 70, 25, 50, 75),
    y = c(5, 15, 25, 25, 15, 35, 50, 50, 65, 70, 65)
  ),
  "3-5-2" = data.frame(
    Position = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "ZM", "LM", "ST", "ST"),
    x = c(50, 30, 25, 30, 25, 40, 50, 60, 75, 40, 60),
    y = c(5, 20, 25, 20, 35, 35, 50, 65, 75, 70, 70)
  ),
  "4-2-3-1" = data.frame(
    Position = c("TW", "RV", "IV", "IV", "LV", "ZDM", "ZDM", "RM", "ZOM", "LM", "ST"),
    x = c(60, 100, 75, 45, 20, 46, 76, 90, 60, 30, 60),
    y = c(17, 55, 50, 50, 55, 70, 70, 90, 90, 90, 110)
  )
)



# Calculate the new columns and weighted sum
player_data <- player_data %>%
  mutate(
    # Assume these columns already exist or are calculated as part of previous steps
    # playtime_ratio: Spielzeit / (90 * max_matchday)
    # avg_playtime_per_game: Spielzeit / (Spiele * 90)
    # points_per_game: (Tore + Assists) / Spiele
    # best_player_ratio: "best player" appearances / Spiele
    # normalized_points_per_game: points_per_game / 3
    
    # Calculate the weighted sum of the specified metrics
    weighted_score = round(
      (playtime_ratio * weight_playtime_ratio) +
        (avg_playtime_per_game * weight_avg_playtime_ratio) +
        (points_per_game * weight_scorerpoints_per_game) +
        (best_player_ratio * weight_best_player_ratio) +
        (normalized_points_per_game * weight_normalized_points_per_game),
      3  # Round to 3 decimal places
    )
  )


# Function to determine formation based on the 'squad' column
extract_formation_and_subs <- function(squad) {
  
  # Step 1: Count the number of substitutions, including multiple names in parentheses
  substitution_count <- sum(str_count(str_extract_all(squad, "\\([^\\)]+\\)")[[1]], ",") + 1)
  
  # Step 2: Remove all names and symbols within parentheses
  squad_cleaned <- str_remove_all(squad, "\\([^\\)]+\\)")
  
  # Step 3: Split the cleaned squad string by "–" to separate each line of players
  lines <- str_split(squad_cleaned, "–")[[1]]
  
  # Step 4: Initialize a list to store player counts for each line
  player_counts <- c()
  
  # Step 5: Process each line to count players based on commas
  for (line in lines[-1]) {  # Exclude the goalkeeper (first element)
    players_in_line <- str_count(line, ",") + 1
    player_counts <- c(player_counts, players_in_line)
  }
  
  # Step 6: Check if the player count adds up to 10
  if (sum(player_counts) == 10) {
    formation <- paste(player_counts, collapse = "-")
  } else {
    formation <- "formation unclear"
  }
  
  return(list(formation = formation, substitutions = substitution_count))
}

# Apply the function to the dataset
# Assuming 'data' is the name of your dataset with a 'squad' column
matchday_data <- matchday_data %>%
  mutate(
    formation = sapply(squad, function(x) extract_formation_and_subs(x)$formation),
    substitutions = sapply(squad, function(x) extract_formation_and_subs(x)$substitutions)
  )


# Define common formations and corresponding position mappings
formations <- list(
  "4-4-2" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-4-1-1" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-2-2-2" = c("TW", "RV", "IV", "IV", "LV", "ZM", "ZM", "RM", "LM", "ST", "ST"),
  "4-3-3" = c("TW", "RV", "IV", "IV", "LV", "ZM", "ZM", "ZM", "RF", "CF", "LF"),
  "3-5-2" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-2-3-1" = c("TW", "RV", "IV", "IV", "LV", "ZDM", "ZDM", "RM", "ZOM", "LM", "ST"),
  "4-1-3-2" = c("TW", "RV", "IV", "IV", "LV", "ZDM","RM", "ZOM", "LM", "ST", "ST"),
  "5-3-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZM", "ZM", "ZM", "ST", "ST"),
  "3-4-3" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "LM", "ST", "ST", "ST"),
  "4-1-4-1" = c("TW", "RV", "IV", "IV", "LV", "ZDM", "RM", "ZOM", "ZOM", "LM", "ST"),
  "3-4-1-2" = c("TW", "IV", "IV", "IV", "RM", "ZDM", "ZDM", "LM", "ZOM", "ST", "ST"),
  "4-5-1" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "ZM", "LM", "ST"),
  "5-4-1" = c("TW", "RV", "IV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST"),
  "5-2-1-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZDM", "ZDM", "ZOM", "ST", "ST"),
  "5-1-2-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZDM", "ZOM", "ZOM", "ST", "ST"),
  "3-2-3-2" = c("TW", "IV", "IV", "IV", "ZDM", "ZDM", "RM", "ZOM", "LM", "ST", "ST"),
  "3-6-1" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "ZM", "ZM", "LM", "ST")
)

# # Step 1: Get unique formations played in the dataset
# played_formations <- unique(data$formation)
# 
# # Step 2: Identify formations not in the current `formations` list
# missing_formations <- setdiff(played_formations, names(formations))
# 
# # Step 3: Automatically add missing formations to `formations` with placeholders
# for (formation in missing_formations) {
#   # Split formation string (e.g., "4-2-3-1") into numbers
#   formation_counts <- as.numeric(str_split(formation, "-")[[1]])
#   
#   # Create a placeholder position list with generic positions
#   position_names <- c("TW", rep("DF", formation_counts[1] - 1),    # Goalkeeper and defenders
#                       rep("MF", formation_counts[2]),              # Midfielders
#                       ifelse(length(formation_counts) > 2,         # Optional attacking midfielders/wingers
#                              rep("AM", formation_counts[3]), NULL),
#                       rep("ST", formation_counts[length(formation_counts)]))  # Strikers
#   
#   # Add this placeholder formation to the formations list
#   formations[[formation]] <- position_names
# }
# 
# print(missing_formations)
# 
# # Check to see all formations are now included
# print("All formations covered in the formations list:")
# print(formations)



# Step 1: Assign positions based on the formation
assign_positions_by_formation <- function(formation, squad) {
  positions <- formations[[formation]]
  if (is.null(positions)) {
    return(rep(NA, length(str_split(squad, ",\\s*|–")[[1]])))
  }
  
  # Split players and remove everything inside parentheses for each player
  players <- str_split(squad, ",\\s*|–")[[1]]
  players <- str_trim(str_remove_all(players, "\\(.*?\\)"))  # Remove text inside parentheses for each player
  
  # Assign positions up to the length of players
  positions[1:length(players)]
}

# Step 2: Process each match to assign positions to players
player_positions <- matchday_data %>%
  filter(formation != "formation unclear") %>%
  rowwise() %>%
  mutate(
    positions = list(assign_positions_by_formation(formation, squad)),
    players = list(str_split(squad, ",\\s*|–")[[1]])
  ) %>%
  unnest(c(players, positions)) %>%
  mutate(players = str_trim(str_remove(players, "\\(.*\\)"))) %>%
  select(matchday, team, players, positions)

# Step 3: Determine each player's most and second most frequent positions
position_frequencies <- player_positions %>%
  group_by(players, positions) %>%
  summarise(n = n(), .groups = "drop") %>%                  # Count occurrences of each position for each player
  arrange(players, desc(n), positions) %>%
  group_by(players) %>%
  slice_head(n = 2) %>%                                     # Keep only the top 2 positions per player
  mutate(rank = row_number()) %>%                           # Rank the top positions
  ungroup() %>%
  spread(key = rank, value = positions, fill = NA) %>%      # Create separate columns for the top 2 positions
  rename(most_position = `1`, second_position = `2`) %>%
  group_by(players) 
position_frequencies <- position_frequencies %>%
  group_by(players) %>%
  summarise(
    most_position = last(most_position),                 # Most frequently played position
    most_position_count = last(n),                       # Count of appearances in most_position
    second_position = first(second_position),             # Second most frequently played position
    second_position_count = ifelse(is.na(second_position), 0, first(n)) # Count of appearances in second_position or 0 if NA
  ) %>%
  arrange(players)  # Arrange by player names


# Step 4: Join with `player_data` and calculate the position percentages
player_data <- player_data %>%
  mutate(last_name = word(Name, -1)) %>%
  left_join(position_frequencies, by = c("last_name" = "players")) %>%
  mutate(
    position_percentage = ifelse(Spiele == 0, 0, paste0(round((most_position_count / Spiele) * 100), "%")),
    second_position_percentage = ifelse(Spiele == 0 | is.na(second_position_count), 
                                        "0%", paste0(round((second_position_count / Spiele) * 100), "%"))
  ) %>%
  select(-last_name, -most_position_count, -second_position_count)  # Remove helper columns

# Function to create an accurate league table by ignoring "away" rows and renaming columns
create_league_table <- function(matchday_data) {
  
  # Rename columns for clarity
  colnames(matchday_data) <- c("matchday", "team", "opponent", "goals_for", "goals_against", "location")
  
  # Filter to only include "home" rows to avoid double counting games
  data <- matchday_data[matchday_data$location == "home", ]
  
  # Initialize the league table with all teams and renamed columns
  teams <- unique(c(matchday_data$team, matchday_data$opponent))
  league_table <- data.frame(
    team = teams,
    S = 0,
    G = 0,
    U = 0,
    V = 0,
    G_h = 0,
    U_h = 0,
    V_h = 0,
    G_a = 0,
    U_a = 0,
    V_a = 0,
    T = 0,
    GT = 0,
    Dif = 0,
    Pkt = 0,
    stringsAsFactors = FALSE
  )
  
  # Process each unique match to update stats for both teams
  for (i in 1:nrow(matchday_data)) {
    match <- data[i, ]
    
    # Check if both home team and away team are in league_table
    if (!(match$team %in% league_table$team) || !(match$opponent %in% league_table$team)) {
      next # Skip this iteration if team names are missing
    }
    
    # Update stats for the home team
    league_table[league_table$team == match$team, "S"] <- league_table[league_table$team == match$team, "S"] + 1
    league_table[league_table$team == match$team, "T"] <- league_table[league_table$team == match$team, "T"] + match$goals_for
    league_table[league_table$team == match$team, "GT"] <- league_table[league_table$team == match$team, "GT"] + match$goals_against
    
    # Update stats for the away team
    league_table[league_table$team == match$opponent, "S"] <- league_table[league_table$team == match$opponent, "S"] + 1
    league_table[league_table$team == match$opponent, "T"] <- league_table[league_table$team == match$opponent, "T"] + match$goals_against
    league_table[league_table$team == match$opponent, "GT"] <- league_table[league_table$team == match$opponent, "GT"] + match$goals_for
    
    # Determine the outcome and update win/draw/loss for both teams
    if (match$goals_for > match$goals_against) {
      # Home team wins, Away team loses
      league_table[league_table$team == match$team, "G"] <- league_table[league_table$team == match$team, "G"] + 1
      league_table[league_table$team == match$team, "Pkt"] <- league_table[league_table$team == match$team, "Pkt"] + 3
      league_table[league_table$team == match$opponent, "V"] <- league_table[league_table$team == match$opponent, "V"] + 1
      
      # Update home/away distinctions
      league_table[league_table$team == match$team, "G_h"] <- league_table[league_table$team == match$team, "G_h"] + 1
      league_table[league_table$team == match$opponent, "V_a"] <- league_table[league_table$team == match$opponent, "V_a"] + 1
      
    } else if (match$goals_for < match$goals_against) {
      # Home team loses, Away team wins
      league_table[league_table$team == match$team, "V"] <- league_table[league_table$team == match$team, "V"] + 1
      league_table[league_table$team == match$opponent, "G"] <- league_table[league_table$team == match$opponent, "G"] + 1
      league_table[league_table$team == match$opponent, "Pkt"] <- league_table[league_table$team == match$opponent, "Pkt"] + 3
      
      # Update home/away distinctions
      league_table[league_table$team == match$team, "V_h"] <- league_table[league_table$team == match$team, "V_h"] + 1
      league_table[league_table$team == match$opponent, "G_a"] <- league_table[league_table$team == match$opponent, "G_a"] + 1
      
    } else {
      # Draw for both teams
      league_table[league_table$team == match$team, "U"] <- league_table[league_table$team == match$team, "U"] + 1
      league_table[league_table$team == match$team, "Pkt"] <- league_table[league_table$team == match$team, "Pkt"] + 1
      league_table[league_table$team == match$opponent, "U"] <- league_table[league_table$team == match$opponent, "U"] + 1
      league_table[league_table$team == match$opponent, "Pkt"] <- league_table[league_table$team == match$opponent, "Pkt"] + 1
      
      # Update home/away distinctions for draws
      league_table[league_table$team == match$team, "U_h"] <- league_table[league_table$team == match$team, "U_h"] + 1
      league_table[league_table$team == match$opponent, "U_a"] <- league_table[league_table$team == match$opponent, "U_a"] + 1
    }
  }
  
  # Calculate Goal Difference
  league_table$Dif <- league_table$T - league_table$GT
  
  # Sort the table by Points (Pkt), Goal Difference (Dif), Goals For (T)
  league_table <- league_table[order(-league_table$Pkt, -league_table$Dif, -league_table$T), ]
  
  # Add Rank column as the first column
  league_table <- data.frame(rank = 1:nrow(league_table), league_table)
  
  return(league_table)
}

# Generate the league table from your data
league_table <- create_league_table(data)

```
```{r, echo = FALSE, results='markup'}

MeinTeam <- "Berliner SC II"
Gegner <- "TSV Rudow Berlin"

```
<br>
<button class="accordion">
  <h2 id="#Spiele">Spiele</h2>
</button>
<div class="panel">
  <p>
```{R echo = FALSE, results='markup'}
# Display the second-to-last nine rows with only the first five columns
display_second_last_nine <- function(matchday_data) {
  # Calculate the index range for the second-to-last nine rows
  start_index <- nrow(matchday_data) - 16 + 1
  end_index <- nrow(matchday_data) - 8
  
  # Extract the second-to-last nine rows and the first five columns
  second_last_nine <- matchday_data[start_index:end_index, 1:5]
  
}

# Apply the function to the league table to display the specified rows and columns
games <- display_second_last_nine(matchday_data)

formatted_games <- formattable(games %>% select(matchday, team, opponent, goals_s, goals_c),
                               align = c("c", "l", "l", "c", "c") 
                     )
colnames(formatted_games)[colnames(formatted_games) %in% c("matchday", "team", "opponent", "goals_s", "goals_c")] <- c("Spieltag", "Team 1", "Team 2", "H", "A") 

# Display the formatted table without row indices
formatted_games




#  # Display the formatted table without row indices
# formatted_games %>%
#   kbl(align = c("c", "l", "l","c", "c")) %>%
#   kable_material_dark("hover", full_width = T,bootstrap_options = c("striped", "hover", "responsive")) %>%
#   kable_styling(font_size = 15, position = "center") 
# 


```
  </p>
</div>
<button class="accordion">
  <h2 id="#Tabelle">Tabelle</h2>
</button>
<div class="panel">
  <p>
```{R echo = FALSE, results='markup'}

league_table_dt <- as.data.table(league_table %>% select(rank, team, S, G, U, V, Dif, Pkt))

# Use formattable to apply color formatting for ranks
formatted_table <- formattable(league_table_dt %>% select(rank, team, S, G, U, V, Dif, Pkt),
                               align = c("c", "l", "c", "c", "c", "c", "c", "c") , 
                               list(
  # Entire row color based on rank
  rank = formatter("span", 
                   style = x ~ style(
                     display = "block",
                     padding = "5px",
                     `border-radius` = "4px",
                     background = ifelse(
                       x == 1, "lightgreen",
                       ifelse(x == 2, "orange",
                              ifelse(x >= (nrow(league_table) - 2), "lightsalmon", "transparent"))
                     ),
                     color = ifelse(
                       x == 1, "black",
                       ifelse(x == 2, "black",
                              ifelse(x >= (nrow(league_table) - 2), "white",  "white"))
                     )
                   )
  ),
  team = formatter("span", 
                 style = x ~ style(
                   display = "block",
                   padding = "5px",
                   `border-radius` = "4px",
                   background = ifelse(
                     x == MeinTeam, "yellow",
                     ifelse(x == Gegner, "yellow",  "transparent")
                   ),
                   color = ifelse(
                     x == MeinTeam, "black",   # Set text color for MeinTeam
                     ifelse(x == Gegner, "black", "white")  # Set text color for Gegner and others
                   )
                 )
  )
))

# Display the formatted table without row indices
formatted_table
#, row.names = FALSE)



```
  </p>
</div>
<body>
<script>
    function navigateToTeam() {
        // Get the selected team's value
        const selectedTeam = document.getElementById("teamSelect").value;
        if (selectedTeam) {
            // Redirect to the selected page
            window.location.href = selectedTeam;
        } else {
            alert("Please select a team!");
        }
    }
    function showLogo() {
        // Get the selected option in the dropdown
        const teamSelect = document.getElementById("teamSelect");
        const selectedOption = teamSelect.options[teamSelect.selectedIndex];
        // Get the logo's path from the data-logo attribute
        const logoPath = selectedOption.getAttribute("data-logo");
        // Update the image or hide it
        const teamLogo = document.getElementById("teamLogo");
        if (logoPath) {
            teamLogo.src = logoPath;
            teamLogo.style.display = "block";
        } else {
            teamLogo.style.display = "none";
        }
    }
</script>
