---
title: "Analyse"
output: html_document
date: "2025-01-08"
---

```{r setup, include=FALSE}
# Setzt den Cache auf FALSE für alle Chunks im Dokument
knitr::opts_chunk$set(cache = FALSE)
library(tidyverse)
library(dplyr)
library(data.table)
library(ggplot2)
library(knitr)
library(ggforce)
# Install and load formattable if not already installed
devtools::install_github("haozhu233/kableExtra")
if (!require(formattable)) install.packages("formattable")
library(formattable)
library("kableExtra")

# Define the URL of the csv.gz file and the destination file path
matchday_data <- read_csv("/Users/mkreuschnervsp/Desktop/BSC/Spieltag15.csv")
player_data <- read.table("/Users/mkreuschnervsp/Desktop/BSC/fupa2425_player_data_15.csv", sep=",", header=TRUE, stringsAsFactors = FALSE, fileEncoding = "UTF-8")
player_number <- read.csv("/Users/mkreuschnervsp/Desktop/BSC/player_number.csv")  # Replace with your 

total_games <- 15


```

## Score weighting

```{r include=FALSE}
# Define weights for Score
weight_playtime_ratio <- 0.3
weight_avg_playtime_ratio <- 0.2
weight_scorerpoints_per_game <- 0.1
weight_best_player_ratio <- 0.3
weight_normalized_points_per_game <- 0.1
```



## player_data 

```{r include=FALSE}
max_matchday <- max(matchday_data$matchday)  # Calculate max matchday
# Calculate the new columns and add them to the player data
player_number_info <- player_number %>%
  select(ID, Nummer) 
player_data <- merge(player_data, player_number_info, by = "ID", all.x = TRUE)

player_data <- player_data %>%
  mutate(
    # First column: Spielzeit divided by (90 * max_matchday), or 0 if Spiele is 0
    playtime_ratio = ifelse(Spiele == 0, 0, round(Spielzeit / (90 * max_matchday), 3)),
    
    # Second column: Spielzeit divided by Spiele, then by 90, or 0 if Spiele is 0
    avg_playtime_per_game = ifelse(Spiele == 0, 0, round(Spielzeit / (Spiele * 90), 3)),
    
    # Third column: (Tore + Assists) divided by Spiele, or 0 if Spiele is 0
    scorerpoints_per_game = ifelse(Spiele == 0, 0, round((Tore + Assists) / Spiele, 3))
  )

# Step 1: Extract last names from `Name` in `player_data`
player_data <- player_data %>%
  mutate(last_name = word(Name, -1))  # Extract last word from Name as last name

# Step 2: Extract best players and count appearances from games_data
# Split 'best_players' by comma, remove leading/trailing spaces, and count each player's occurrences
best_player_counts <- matchday_data %>%
  filter(!is.na(best_players)) %>%
  mutate(best_players = str_split(best_players, ",\\s*")) %>%  # Split by comma and trim whitespace
  unnest(best_players) %>%                                      # Expand each player into separate rows
  group_by(best_players) %>%
  summarise(best_player_appearances = n())                      # Count each player's "best player" appearances

# Step 3: Join with player_data using last names and calculate the ratio of "best player" appearances to total games played
player_data <- player_data %>%
  left_join(best_player_counts, by = c("last_name" = "best_players")) %>%  # Join by last name
  mutate(
    best_player_appearances = coalesce(best_player_appearances, 0),        # Replace NA with 0 for players with no appearances
    best_player_ratio = ifelse(Spiele == 0, 0,                             # Calculate ratio; if Spiele is 0, set to 0
                               round(best_player_appearances / Spiele, 3))
  ) %>%
  select(-last_name)  # Remove the last_name helper column if it's no longer needed

# Step 1: Calculate team points based on game results
data <- matchday_data %>%
  mutate(
    team_points = case_when(
      goals_s > goals_c ~ 3,    # 3 points for a win
      goals_s == goals_c ~ 1,   # 1 point for a draw
      goals_s < goals_c ~ 0     # 0 points for a loss
    )
  )

# Step 2: Extract player participation, handling both main players and substitutes
player_participation <- data %>%
  select(matchday, team, squad, team_points) %>%
  
  # Step 2.1: Extract all player names inside parentheses, remove numbers and symbols, and store them
  mutate(substitute_names = str_extract_all(squad, "\\([A-Za-z\\s]+\\)")) %>%
  mutate(substitute_names = lapply(substitute_names, function(x) {
    x <- str_replace_all(x, "[()]", "")           # Remove parentheses
    x <- str_trim(str_squish(x))                  # Trim whitespace
    x <- str_split(x, ",\\s*")                    # Split multiple names by commas
    unlist(x)                                     # Unlist to get all names in a single vector
  })) %>%
  
  # Step 2.2: Remove all content inside parentheses from the original squad string
  mutate(squad = str_remove_all(squad, "\\([^\\)]+\\)")) %>%
  
  # Step 2.3: Split the squad by commas and "–" to get main player names
  mutate(squad = str_split(squad, ",\\s*|–")) %>%
  
  # Step 2.4: Combine main and substitute player names into a single column
  rowwise() %>%
  mutate(all_players = list(c(squad, substitute_names))) %>%
  unnest(all_players) %>%                                # Expand each player into a separate row
  mutate(
    all_players = str_trim(all_players)                  # Ensure no whitespace issues
  ) %>%
  
  # Step 2.5: Remove duplicates and calculate participation
  distinct(all_players, matchday, .keep_all = TRUE) %>%  # Ensure unique player names for each match
  group_by(all_players) %>%
  summarise(
    total_points = sum(team_points, na.rm = TRUE),       # Sum points for each player's games
    matches_played = n_distinct(matchday)                # Count unique matches played
  ) %>%
  
  # Rename 'all_players' to 'squad' to reflect player names for compatibility with joining
  rename(squad = all_players)

# Step 1: Ensure `last_name` is correctly extracted from `Name` in `player_data`
player_data <- player_data %>%
  mutate(last_name = str_trim(word(Name, -1)))  # Extract and trim last names for matching

# Step 2: Perform the left join and handle missing columns
player_data <- player_data %>%
  left_join(player_participation, by = c("last_name" = "squad")) %>%  # Join on last name
  mutate(
    # Add missing columns if they do not exist after the join
    matches_played = ifelse(is.na(matches_played), 0, matches_played),  # Set to 0 if missing
    total_points = ifelse(is.na(total_points), 0, total_points),        # Set to 0 if missing
    match_diff = Spiele - matches_played,                               # Difference between Spiele and matches_played
    points_per_game = ifelse(matches_played == 0, 0,                    # Calculate points per game
                             round(total_points / matches_played, 3)),
    normalized_points_per_game = round(points_per_game / 3, 3)          # Divide by 3 and round to 3 decimals
  ) %>%
  select(-last_name)  # Remove helper last_name column
```

```{r include=FALSE}
# Calculate the new columns and weighted sum
player_data <- player_data %>%
  mutate(
    weighted_score = round(
      (playtime_ratio * weight_playtime_ratio) +
        (avg_playtime_per_game * weight_avg_playtime_ratio) +
        (points_per_game * weight_scorerpoints_per_game) +
        (best_player_ratio * weight_best_player_ratio) +
        (normalized_points_per_game * weight_normalized_points_per_game),3  # Round to 3 decimal places
    )
  )

# Function to determine formation based on the 'squad' column
extract_formation_and_subs <- function(squad) {
  
  # Step 1: Count the number of substitutions, including multiple names in parentheses
  substitution_count <- sum(str_count(str_extract_all(squad, "\\([^\\)]+\\)")[[1]], ",") + 1)
  
  # Step 2: Remove all names and symbols within parentheses
  squad_cleaned <- str_remove_all(squad, "\\([^\\)]+\\)")
  
  # Step 3: Split the cleaned squad string by "–" to separate each line of players
  lines <- str_split(squad_cleaned, "–")[[1]]
  
  # Step 4: Initialize a list to store player counts for each line
  player_counts <- c()
  
  # Step 5: Process each line to count players based on commas
  for (line in lines[-1]) {  # Exclude the goalkeeper (first element)
    players_in_line <- str_count(line, ",") + 1
    player_counts <- c(player_counts, players_in_line)
  }
  
  # Step 6: Check if the player count adds up to 10
  if (sum(player_counts) == 10) {
    formation <- paste(player_counts, collapse = "-")
  } else {
    formation <- "formation unclear"
  }
  
  return(list(formation = formation, substitutions = substitution_count))
}

# Apply the function to the dataset
# Assuming 'data' is the name of your dataset with a 'squad' column
matchday_data <- matchday_data %>%
  mutate(
    formation = sapply(squad, function(x) extract_formation_and_subs(x)$formation),
    substitutions = sapply(squad, function(x) extract_formation_and_subs(x)$substitutions)
  )


# Define common formations and corresponding position mappings
formations_positions <- list(
  "4-4-2" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-4-1-1" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-2-2-2" = c("TW", "RV", "IV", "IV", "LV", "ZM", "ZM", "RM", "LM", "ST", "ST"),
  "4-3-3" = c("TW", "RV", "IV", "IV", "LV", "ZM", "ZM", "ZM", "RM", "ST", "LM"),
  "3-5-2" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "ZM", "LM", "ST", "ST"),
  "4-2-3-1" = c("TW", "RV", "IV", "IV", "LV", "ZDM", "ZDM", "RM", "ZOM", "LM", "ST"),
  "4-1-3-2" = c("TW", "RV", "IV", "IV", "LV", "ZDM","RM", "ZOM", "LM", "ST", "ST"),
  "5-3-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZM", "ZM", "ZM", "ST", "ST"),
  "3-4-3" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "LM", "ST", "ST", "ST"),
  "4-1-4-1" = c("TW", "RV", "IV", "IV", "LV", "ZDM", "RM", "ZOM", "ZOM", "LM", "ST"),
  "3-4-1-2" = c("TW", "IV", "IV", "IV", "RM", "ZDM", "ZDM", "LM", "ZOM", "ST", "ST"),
  "4-5-1" = c("TW", "RV", "IV", "IV", "LV", "RM", "ZM", "ZM", "ZM", "LM", "ST"),
  "5-4-1" = c("TW", "RV", "IV", "IV", "IV", "LV", "RM", "ZM", "ZM", "LM", "ST"),
  "5-2-1-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZDM", "ZDM", "ZOM", "ST", "ST"),
  "5-1-2-2" = c("TW", "RV", "IV", "IV", "IV", "LV", "ZDM", "ZOM", "ZOM", "ST", "ST"),
  "3-2-3-2" = c("TW", "IV", "IV", "IV", "ZDM", "ZDM", "RM", "ZOM", "LM", "ST", "ST"),
  "3-6-1" = c("TW", "IV", "IV", "IV", "RM", "ZM", "ZM", "ZM", "ZM", "LM", "ST")
)

# Step 1: Assign positions based on the formation
assign_positions_by_formation <- function(formation, squad) {
  positions <- formations_positions[[formation]]  # "formations" ersetzt durch "formations_positions"
  if (is.null(positions)) {
    return(rep(NA, length(str_split(squad, ",\\s*|\u2013")[[1]])))
  }

  # Split players and remove everything inside parentheses for each player
  players <- str_split(squad, ",\\s*|\u2013")[[1]]
  players <- str_trim(str_remove_all(players, "\\(.*?\\)"))  # Remove text inside parentheses for each player

  # Assign positions up to the length of players
  positions[1:length(players)]
}

# Step 2: Process each match to assign positions to players
player_positions <- matchday_data %>%
  filter(formation != "formation unclear") %>%
  rowwise() %>%
  mutate(
    positions = list(assign_positions_by_formation(formation, squad)),
    players = list(str_split(squad, ",\\s*|\u2013")[[1]])
  ) %>%
  unnest(c(players, positions)) %>%
  mutate(players = str_trim(str_remove(players, "\\(.*\\)"))) %>%
  select(matchday, team, players, positions)

# Step 3: Determine each player's most and second most frequent positions
position_frequencies <- player_positions %>%
  group_by(players, positions) %>%
  summarise(n = n(), .groups = "drop") %>%                  # Count occurrences of each position for each player
  arrange(players, desc(n), positions) %>%
  group_by(players) %>%
  slice_head(n = 2) %>%                                     # Keep only the top 2 positions per player
  mutate(rank = row_number()) %>%                           # Rank the top positions
  ungroup() %>%
  spread(key = rank, value = positions, fill = NA) %>%      # Create separate columns for the top 2 positions
  rename(most_position = `1`, second_position = `2`) %>%
  group_by(players)

position_frequencies <- position_frequencies %>%
  group_by(players) %>%
  summarise(
    most_position = last(most_position),                 # Most frequently played position
    most_position_count = last(n),                       # Count of appearances in most_position
    second_position = first(second_position),             # Second most frequently played position
    second_position_count = ifelse(is.na(second_position), 0, first(n)) # Count of appearances in second_position or 0 if NA
  ) %>%
  arrange(players)  # Arrange by player names

# Step 4: Join with `player_data` and calculate the position percentages
player_data <- player_data %>%
  mutate(last_name = word(Name, -1)) %>%
  left_join(position_frequencies, by = c("last_name" = "players")) %>%
  mutate(
    position_percentage = ifelse(Spiele == 0, 0, paste0(round((most_position_count / Spiele) * 100), "%")),
    second_position_percentage = ifelse(Spiele == 0 | is.na(second_position_count), 
                                        "0%", paste0(round((second_position_count / Spiele) * 100), "%"))
  ) %>%
  select(-last_name, -most_position_count, -second_position_count)  # Remove helper columns


```



## tabellen
```{R echo = FALSE, results='markup'}

# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
gesamttabelle <- matchday_data %>%
    #filter(where == "home") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
gesamttabelle <- gesamttabelle %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben
  
# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
heimtabelle <- matchday_data %>%
    filter(where == "home") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
heimtabelle <- heimtabelle %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben


# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
auswärtstabelle <- matchday_data %>%
    filter(where == "away") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
auswärtstabelle <- auswärtstabelle %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben

# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
rasentabelle <- matchday_data %>%
    filter(size == "NR") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
rasentabelle  <- rasentabelle  %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben

# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
kunstrasentabelle <- matchday_data %>%
    filter(size != "NR") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
kunstrasentabelle  <- kunstrasentabelle  %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben


# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
kleinkunstrasentabelle <- matchday_data %>%
    filter(size == "S") %>%
    filter(!is.na(goals_s) & !is.na(goals_c))
  
# Aggregation: Berechnung von Siegen, Unentschieden, Niederlagen, Toren, Gegentoren
kleinkunstrasentabelle  <- kleinkunstrasentabelle  %>%
    group_by(team) %>%
    summarise(
      S = n(),
      G = sum(goals_s > goals_c),
      U = sum(goals_s == goals_c),
      N = sum(goals_s < goals_c),
      Tore = paste(sum(goals_s),sum(goals_c),sep =":"),
      Dif = sum(goals_s) - sum(goals_c)
    ) %>%
    mutate(
      Pkt = G * 3 + U    # Punkte berechnen
    ) %>%
    arrange(desc(Pkt), desc(Dif)) %>%  # Tabelle nach Punkten und Differenz sortieren
    mutate("#" = row_number()) %>%             # Rank-Spalte hinzufügen
    select("#", everything())                  # Rank-Spalte an den Anfang verschieben

```


## spieltage
```{R echo = FALSE, results='markup'}
# Filter nur für Heimspiele ("home") und nur Spiele, bei denen Ergebnisse vorhanden sind
all_games <- matchday_data %>%
  filter(where == "home")              # Nur Heimspiele

# Ergebnis-Spalte (z.B. "1:0") erstellen
all_games <- all_games %>%
  mutate(Ergebnis = paste(goals_s, goals_c, sep = ":"))

# Nur die letzten 5 Spiele basierend auf Spieltag auswählen
all_games <- all_games %>%
  arrange(desc(matchday)) 

# Spalten umbenennen
all_games <- all_games %>%
  select(
    Spieltag = matchday,
    Heim = team,
    Auswärts = opponent,
    Ergebnis
  )

# Hinspiel-Spalte erstellen
all_games <- all_games %>%
  rowwise() %>%
  mutate(
    Hinspiel = if (Spieltag <= 15) {
      # Wenn Spieltag <= 15: dasselbe Ergebnis wie in Spalte "Ergebnis"
      Ergebnis
    } else {
      # Wenn Spieltag > 15: Suche das Hinrundenergebnis (umgekehrte Spielpaarung zwischen Spieltag 1 und 15)
      hinrunde_match <- all_games %>%
        filter(Spieltag <= 15 & Heim == Auswärts & Auswärts == Heim)
      
      if (nrow(hinrunde_match) > 0) {
        paste0("(", hinrunde_match$goals_c, ":", hinrunde_match$goals_s, ")")
      } else {
        "-"
      }
    }
  )

replace_na_in_column <- function(data, column_name, replacement = "-") {
  data[[column_name]] <- ifelse(is.na(data[[column_name]]), replacement, data[[column_name]])
  return(data)
}

all_games <- replace_na_in_column(all_games , "Ergebnis", "-")


```

## letzte 5 Spiele
```{R echo = FALSE, results='markup'}

# Filter nur für Heimspiele ("home") und nur Spiele, bei denen Ergebnisse vorhanden sind
last_five_games <- matchday_data %>%
  filter(where == "home") %>%               # Nur Heimspiele
  filter(!is.na(goals_s) & !is.na(goals_c)) # Nur gespielte Spiele

# Nur die letzten 5 Spiele basierend auf Spieltag auswählen
last_five_games <- last_five_games %>%
  arrange(desc(matchday)) %>%               # Nach Spieltag absteigend sortieren
  slice_head(n = 40)                         # Nur die letzten 5 Spiele

# Ergebnis-Spalte (z.B. "1:0") erstellen
last_five_games <- last_five_games %>%
  mutate(Ergebnis = paste(goals_s, goals_c, sep = ":"))

# Spalten umbenennen
last_five_games <- last_five_games %>%
  select(
    Spieltag = matchday,
    Heim = team,
    Auswärts = opponent,
    Ergebnis
  )

# Hinspiel-Spalte erstellen
last_five_games <- last_five_games %>%
  rowwise() %>%
  mutate(
    Hinspiel = if (Spieltag <= 15) {
      # Wenn Spieltag <= 15: dasselbe Ergebnis wie in Spalte "Ergebnis"
      Ergebnis
    } else {
      # Wenn Spieltag > 15: Suche das Hinrundenergebnis (umgekehrte Spielpaarung zwischen Spieltag 1 und 15)
      hinrunde_match <- filtered_data %>%
        filter(matchday <= 15 & Heim == Auswärts & Auswärts == Heim)
      
      if (nrow(hinrunde_match) > 0) {
        paste0("(", hinrunde_match$goals_c, ":", hinrunde_match$goals_s, ")")
      } else {
        NA
      }
    }
  )

```

## formtabelle
```{R echo = FALSE, results='markup'}

# Filter nur für Heimspiele und Spiele mit gültigen Ergebnissen
last_five_games_1 <- matchday_data %>%
  filter(!is.na(goals_s) & !is.na(goals_c)) %>% # Nur gespielte Spiele
  arrange(desc(matchday)) %>%               # Nach Spieltag absteigend sortieren
  slice_head(n = 80)                         # Nur die letzten 5 Spiele
   
formtabelle <- last_five_games_1 %>%
  group_by(team) %>%
  arrange(team, desc(matchday)) %>%  # Sortiere nach Team und Spieltag absteigend
  mutate(
    Ergebnis = case_when(
      goals_s > goals_c ~ "S",  # Sieg
      goals_s == goals_c ~ "U", # Unentschieden
      goals_s < goals_c ~ "N"   # Niederlage
    ),
    Punkte = case_when(
      goals_s > goals_c ~ 3,    # 3 Punkte für Sieg
      goals_s == goals_c ~ 1,   # 1 Punkt für Unentschieden
      goals_s < goals_c ~ 0     # 0 Punkte für Niederlage
    )
  ) %>%
  summarise(
    Spiele = n(),
    "Letzte Spiele" = paste(Ergebnis[5],Ergebnis[4],Ergebnis[3],Ergebnis[2],Ergebnis[1] , sep = "-" ),
    Tore = paste(sum(goals_s),sum(goals_c),sep = ":"),
    Dif = sum(goals_s)- sum(goals_c),
    Pkt = round(mean(Punkte, na.rm = TRUE), 3)  # Durchschnittspunkte berechnen
  ) %>%
  arrange(desc(Pkt), desc(Dif))  # Tabelle nach Durchschnittspunkten und Differenz sortieren


```


## formation mit Gewichtung
```{R echo = FALSE, results='markup'} 

extract_formation_and_subs <- function(squad) {
  
  # Step 1: Count the number of substitutions, including multiple names in parentheses
  substitution_count <- sum(str_count(str_extract_all(squad, "\\([^\\)]+\\)")[[1]], ",") + 1)
  
  # Step 2: Remove all names and symbols within parentheses
  squad_cleaned <- str_remove_all(squad, "\\([^\\)]+\\)")
  
  # Step 3: Split the cleaned squad string by "–" to separate each line of players
  lines <- str_split(squad_cleaned, "–")[[1]]
  
  # Step 4: Initialize a list to store player counts for each line
  player_counts <- c()
  
  # Step 5: Process each line to count players based on commas
  for (line in lines[-1]) {  # Exclude the goalkeeper (first element)
    players_in_line <- str_count(line, ",") + 1
    player_counts <- c(player_counts, players_in_line)
  }
  
  # Step 6: Check if the player count adds up to 10
  if (sum(player_counts) == 10) {
    formation <- paste(player_counts, collapse = "-")
  } else {
    formation <- "formation unclear"
  }
  
  return(list(formation = formation, substitutions = substitution_count))
}

# Apply the function to the dataset
# Assuming 'data' is the name of your dataset with a 'squad' column
formation_data <- matchday_data %>%
  mutate(
    formation = sapply(squad, function(x) extract_formation_and_subs(x)$formation),
    substitutions = sapply(squad, function(x) extract_formation_and_subs(x)$substitutions)
  )

formation_data <- formation_data %>%
  select(
    Spieltag = matchday,
    Team = team,
    Gegner = opponent,
    Tore = goals_s,
    Gegentore = goals_c,
    Wo = where, 
    Platz = size,
    Kader = squad,
    Formation = formation,
    Wechsel = substitutions
  )

```

Graphen/Tabelle: Formationen, Formation bei Siegen, Formation auf Plätzen, Formation H/A, Wechselanzahl pro Spiel
letzte 5 Formationen

## Tore
```{R echo = FALSE, results='markup'}

# Function to extract and organize goalscorer data from the dataset
extract_goalscorer_data <- function(data) {
  
  # Step 1: Filter out rows where 'goalscorer' column is NA or empty
  data <- matchday_data %>% filter(!is.na(goalscorer) & goalscorer != "")
  
  # Step 2: Split multiple scorers within each 'goalscorer' entry into separate rows
  data <- matchday_data %>%
    separate_rows(goalscorer, sep = ";\\s*")  # Split on ";" or "; " (semicolon with or without a space)
  
  # Step 3: Extract and organize information for each scorer
  data <- data %>%
    mutate(
      # Extract the score in the format "1:2" at the beginning of the string
      score = str_extract(goalscorer, "^\\d+:\\d+"),
      
      # Extract main minute and additional time, handling cases like (76.), (45+2.), (90+5.), and (90. +2)
      minute_full = str_extract(goalscorer, "\\((\\d+\\.? ?\\+?\\d*)\\)"),
      
      # Separate main minute and additional time
      minute = str_extract(minute_full, "\\d+") %>% as.numeric(),  # Extract main minute
      additional_time = str_extract(minute_full, "\\+?\\d+") %>%   # Extract additional time if present
        str_replace("\\+", "") %>%
        as.numeric(),
      
      # Extract the scorer's name after removing score and minute components
      scorer = str_trim(str_replace(goalscorer, "^\\d+:\\d+ \\(.*?\\)", ""))
    ) %>%
    
    # Step 4: Select relevant columns for the final dataset
    select(scorer, team, opponent, minute, score)
  
    # Step 5: Filter out rows where 'goalscorer' column is NA or empty
    data <- data %>% filter(!is.na(minute) & minute != "")
  
  return(data)
}

# Apply the function to your dataset
goals_data <- extract_goalscorer_data(matchday_data)


```


Säulendiagramm - wann Tore gefallen sind - Team
Säulendiagramm - wann Tore gefallen sind - insgesamt

Tabelle, welche Position die Tore geschossen hat


## Score from player_data
```{R echo = FALSE, results='markup'}

# Filter, sort, and select the top 5 players by weighted score
score_data <- player_data %>%                    # Filter by the specified team
  arrange(desc(weighted_score)) %>% 
  filter(Spiele / total_games >= 0.25)

# Add a Rank column to the top_scorers data frame
score_data <- score_data %>%
  mutate(Rank = row_number()) %>%
  select(Rank, 
         Nr = Nummer, 
         Name, 
         Pos = most_position, 
         Spielzeit,
         Score = weighted_score)  # Select desired columns

```

## Torschützen from player_data
```{R echo = FALSE, results='asis'}
# Filter, sort, and select the top 5 players by scorerpoints_per_game
goalscorer <- player_data %>%
  arrange(desc(Tore))               # Sort by Scorerpoints per game in descending order

# Add a Rank column to the top_scorers data frame
goalscorer_data <- goalscorer %>%
  mutate(Rank = row_number()) %>%
  select(Rank, 
         Name,
         Nr = Nummer,
         Pos = most_position, 
         Spiele, 
         Tore)  # Select desired columns

```


## Assists from player_data
```{R echo = FALSE, results='asis'}

# Filter, sort, and select the top 5 players by scorerpoints_per_game
assists <- player_data %>%
  arrange(desc(Assists))

# Add a Rank column to the top_scorers data frame
assists_data <- assists %>%
  mutate(Rank = row_number()) %>%
  select(Rank, 
         Name,
         Nr = Nummer, 
         Pos = most_position, 
         Spiele, 
         Assists)  # Select desired columns

```


## Scorerpoints from player_data
```{R echo = FALSE, results='asis'}


# Filter, sort, and select the top 5 players by scorerpoints_per_game
scorerpoints_data <- player_data %>%
  filter(Spiele / total_games >= 0.25) %>% # Filter by the specified team
  arrange(desc(scorerpoints_per_game))          # Sort by Scorerpoints per game in descending order


# Add a Rank column to the top_scorers data frame
scorerpoints_data <- scorerpoints_data %>%
  mutate(Rank = row_number()) %>%
  select(Rank, 
         Name, 
         Nr = Nummer,  
         Pos = most_position, 
         Spiele,
         Scorerpoints = scorerpoints_per_game
         )  # Select desired columns

```

## erwartete S11
```{R echo = FALSE, results='markup'}

# Part 1: Find the Most Used Formation
most_used_formations <- formation_data %>%
  filter(!is.na(Tore) & !is.na(Gegentore)) %>% 
  group_by(Team) %>%                           # Gruppiere nach Team
  count(Formation, name = "Anzahl") %>%        # Zähle die Vorkommen jeder Formation pro Team
  arrange(Team, desc(Anzahl)) %>%              # Sortiere nach Team und Anzahl (absteigend)
  slice_head(n = 1) %>%                        # Wähle für jedes Team die häufigste Formation aus
  ungroup()                                    # Gruppierung aufheben

# Schritt 1: Berechnung der Wahrscheinlichkeit pro Formation
formation_probabilities <- formation_data %>%
  filter(!is.na(Tore) & !is.na(Gegentore)) %>% 
  group_by(Team, Formation) %>%
  summarise(
    Anzahl = n(),                           # Anzahl der Spiele mit dieser Formation
    .groups = "drop"
  ) %>%
  group_by(Team) %>%
  mutate(
    Total_Spiele = sum(Anzahl),             # Gesamtanzahl der Spiele pro Team
    Wahrscheinlichkeit = paste0(round((Anzahl / Total_Spiele) * 100), "%"),  # Wahrscheinlichkeit in %
    dreier_kette = ifelse(startsWith(Formation, "3"), "Ja", "Nein"),  # "Ja" für "3", sonst "Nein"
    vierer_kette = ifelse(startsWith(Formation, "4"), "Ja", "Nein")   # "Ja" für "4", sonst "Nein"
  ) %>%
  ungroup()

starting_11_all_teams <- formation_probabilities %>%
  rowwise() %>%
  mutate(
    Starting11 = list({
      formation_positions_current <- unlist(formations_positions[[Formation]])
      occupied_positions <- character(0)
      expected_squad <- data.frame()

      # Filtere Spieler für das aktuelle Team aus der Formation
      current_team <- Team  # Referenz auf das Team der aktuellen Zeile
      team_players <- player_data %>%
        filter(Team == current_team) %>%  # Nur Spieler des aktuellen Teams
        arrange(desc(weighted_score))

      # Iterative Zuweisung der Spieler zu Positionen
      for (i in 1:nrow(team_players)) {
        player <- team_players[i, ]
        player_positions <- c(as.character(player$most_position), as.character(player$second_position))

        for (position in player_positions) {
          position <- as.character(position)
          if (position %in% formation_positions_current &&
              sum(occupied_positions == position) < sum(formation_positions_current == position)) {
            expected_squad <- rbind(expected_squad,
                                    data.frame(
                                      Team = player$Team,
                                      Position = position,
                                      Nummer = player$Nummer,
                                      Name = player$Name,
                                      Weighted_Score = player$weighted_score
                                    ))
            occupied_positions <- c(occupied_positions, position)
            break
          }
        }

        if (nrow(expected_squad) == length(formation_positions_current)) {
          break
        }
      }
      expected_squad
    })
  ) %>%
  unnest(Starting11, names_sep = "_")

```


## head2head 
```{R echo = FALSE, results='markup'}

formation_per_team <- formation_probabilities %>%
  rename(team = Team) %>%
  group_by(team) %>%                  # Gruppieren nach Team
  arrange(desc(Anzahl)) %>%           # Sortieren nach Anzahl absteigend
  slice_head(n = 1) %>%               # Die erste Zeile (höchste Anzahl) pro Team auswählen
  ungroup()  # Gruppierung aufheben

abwehrkette <- formation_probabilities %>%
  rename(team = Team) %>%
  group_by(team) %>%
  summarise(dreierKette = ifelse(any(dreier_kette == "Ja"), "Ja", "Nein"),
            viererKette = ifelse(any(vierer_kette == "Ja"), "Ja", "Nein")) %>%
  ungroup()
  
head2head_data <- gesamttabelle %>%
  select(team, "#", G, U, N) %>%
  mutate(
    Ges_Bilanz = paste(G, U, N, sep = "-")  # Bilanz der Gesamttabelle
  ) %>%
  left_join(
    heimtabelle %>%
      mutate(
        H_Bilanz = paste(G, U, N, sep = "-")  # Heim-Bilanz
      ) %>%
      select(team, Rank_H = "#" , H_Bilanz),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz) %>%
  left_join(
    auswärtstabelle %>%
      mutate(
        A_Bilanz = paste(G, U, N, sep = "-")  # Aus-Bilanz
      ) %>%
      select(team, Rank_A = "#" , A_Bilanz),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz) %>%
  left_join(
    rasentabelle %>%
      mutate(
        NR_Bilanz = paste(G, U, N, sep = "-")  # Rasen-Bilanz
      ) %>%
      select(team, Rank_NR = "#" , NR_Bilanz),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz) %>%
  left_join(
    kunstrasentabelle %>%
      mutate(
        KR_Bilanz = paste(G, U, N, sep = "-")  # KuRa-Bilanz
      ) %>%
      select(team, Rank_KR = "#" , KR_Bilanz),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz, Rank_KR, KR_Bilanz) %>%
  left_join(
    kleinkunstrasentabelle %>%
      mutate(
        kKR_Bilanz = paste(G, U, N, sep = "-")  # KuRa-Bilanz
      ) %>%
      select(team, Rank_kKR = "#" , kKR_Bilanz),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz, Rank_KR, KR_Bilanz, Rank_kKR, kKR_Bilanz) %>%
  left_join(
    formtabelle %>%
      select(team, "Letzte Spiele" ,Tore),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz, Rank_KR, KR_Bilanz, Rank_kKR, kKR_Bilanz, "Letzte Spiele" ,Tore) %>%
  left_join(
    formation_per_team %>%
      select(team, Formation , Wahrscheinlichkeit),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz, Rank_KR, KR_Bilanz, Rank_kKR, kKR_Bilanz, "Letzte Spiele" ,Tore, Formation , Wahrscheinlichkeit) %>%
  left_join(
    abwehrkette %>%
      select(team, dreierKette , viererKette),
    by = "team"
  ) %>%
  select(team, "#", Ges_Bilanz, Rank_H, H_Bilanz, Rank_A, A_Bilanz, Rank_NR, NR_Bilanz, Rank_KR, KR_Bilanz, Rank_kKR, kKR_Bilanz, "Letzte Spiele" ,Tore, Formation , Wahrscheinlichkeit, dreierKette , viererKette)

```



## Ausgeben der neuen Datei

Diese werden gebraucht, um die Graphen und Tabellen zu erstellen.

```{r, echo = FALSE, results='markup'}

#tabellen
write_csv(gesamttabelle,file = "~/git/berlinersc-football-analysis.github.io/data/gesamttabelle.csv")
write_csv(heimtabelle,file = "~/git/berlinersc-football-analysis.github.io/data/heimtabelle.csv")
write_csv(auswärtstabelle,file = "~/git/berlinersc-football-analysis.github.io/data/auswaertstabelle.csv")
write_csv(rasentabelle,file = "~/git/berlinersc-football-analysis.github.io/data/rasentabelle.csv")
write_csv(kunstrasentabelle,file = "~/git/berlinersc-football-analysis.github.io/data/kunstrasentabelle.csv")
write_csv(kleinkunstrasentabelle,file = "~/git/berlinersc-football-analysis.github.io/data/kleinkunstrasentabelle.csv")
write_csv(formtabelle,file = "~/git/berlinersc-football-analysis.github.io/data/formtabelle.csv")

write_csv(all_games,file = "~/git/berlinersc-football-analysis.github.io/data/Spieltage.csv")



#player_data
write_csv(player_data,file = "~/git/berlinersc-football-analysis.github.io/data/player_data.csv")

#head2head - neue Tabelle - Hinspiel-Rückspiel-Bilanz-Formation-Tore-GT
write_csv(head2head_data,file = "~/git/berlinersc-football-analysis.github.io/data/head2head.csv")

#letzte 5 Spiele from matchday_data
write_csv(last_five_games,file = "~/git/berlinersc-football-analysis.github.io/data/last5games.csv")

#formation mit Gewichtung
write_csv(formation_data,file = "~/git/berlinersc-football-analysis.github.io/data/formation_data.csv")

#erwartete S11 from player_data
write_csv(starting_11_all_teams,file = "~/git/berlinersc-football-analysis.github.io/data/exp11.csv")

#Tore from matchday_data
write_csv(goals_data,file = "~/git/berlinersc-football-analysis.github.io/data/goals.csv")

#Score from player_data
write_csv(score_data,file = "~/git/berlinersc-football-analysis.github.io/data/best_score.csv")

#Torschützen from player_data
write_csv(goalscorer_data,file = "~/git/berlinersc-football-analysis.github.io/data/goalscorer.csv")

#Assists from player_data
write_csv(assists_data,file = "~/git/berlinersc-football-analysis.github.io/data/assists.csv")

#Scorerpoints from player_data
write_csv(scorerpoints_data,file = "~/git/berlinersc-football-analysis.github.io/data/scorerpoints.csv")

#keypoints -> keypoints
#write(keypoints_data,file = "~/git/berlinersc-football-analysis.github.io/data/keypoints.csv")

```


